An artificial neural network (ANN) is a mathematical model mimicking biological neural networks,
namely their ability to learn and correct errors from previous experience.[Chen, Yung-Yao; Lin, Yu-Hsiu; Kung, Chia-Ching; Chung, Ming-Han;
Yen, I.-Hsuan (January 2019). "Design and Implementation of Cloud Analytics-Assisted Smart Power Meters Considering Advanced Artificial Intelligence as
 Edge Analytics in Demand-Side Management for Smart Homes". Sensors. 19 (9): 2047. doi:10.3390/s19092047. PMC 6539684. PMID 31052502.]
ANN consists of a collection of nodes called neurons, and each node is linked to other nodes via connections called synapses.
ANN is typically divided into an input layer, followed by several hidden layers and an output layer. [5M] \\
The ANN subject was first introduced by Warren McCulloch and Walter Pitts in "A logical calculus of the ideas immanent in nervous activity" published in 1943.[6 M] But it was not until recent years when ANN has gained popularity with still increasing advancements in technology and availability of training data.
ANN had become one of the default solutions for complex tasks which were previously thought be unsolvable by computers. [7M] \\
This chapter will briefly explore different types of neural units and their activation functions, along with some exemplary network architectures.

\setsecnumdepth{all}
\section{Artificial Neuron}
\input{chapters/neural_network/artificial_neuron.tex}
%=======================================================================================================================
\section{Types of Neural Networks}
\input{chapters/neural_network/types_of_nn.tex}
%=======================================================================================================================