% arara: xelatex
% arara: xelatex
% arara: xelatex


% options:
% thesis=B bachelor's thesis
% thesis=M master's thesis
% czech thesis in Czech language
% english thesis in English language
% hidelinks remove colour boxes around hyperlinks

\documentclass[thesis=B,english]{FITthesis}[2020/10/23]

%\usepackage[utf8]{inputenc} % LaTeX source encoded as UTF-8
% \usepackage[latin2]{inputenc} % LaTeX source encoded as ISO-8859-2
% \usepackage[cp1250]{inputenc} % LaTeX source encoded as Windows-1250

% \usepackage{subfig} %subfigures
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols

\usepackage{dirtree} %directory tree visualisation
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage{nameref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pdfpages}

\graphicspath{ {./assets/} }
% % list of acronyms
% \usepackage[acronym,nonumberlist,toc,numberedsection=autolabel]{glossaries}
% \iflanguage{czech}{\renewcommand*{\acronymname}{Seznam pou{\v z}it{\' y}ch zkratek}}{}
% \makeglossaries

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% EDIT THIS
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\department{Department of Theoretical Computer Science}
\title{Gesture detector with Leap Motion sensor}
\authorGN{Viet Anh} %author's given name/names
\authorFN{Tran} %author's surname
\author{Viet Anh Tran} %author's name without academic degrees
\authorWithDegrees{Viet Anh Tran} %author's name with academic degrees
\supervisor{Ing. Tomáš Nováček}

\acknowledgements{First, I would like to thank my supervisor Ing. Tomáš Nováček, for his active support and guidance on and off my studies. I also wish to thank my friends, namely Ája, Nikky, Daniel, David, Matěj, for making the world a bit more colorful and Bc. Matouš Kozák for his never-ending help during my time at the faculty. Finally, to thank my mother for putting up with me my entire life.}


\abstractEN{Exploring ways to control the virtual environment is a popular goal of many human-computer interaction researchers. One of the approaches is using Leap Motion optical sensors, developed specifically to track hand and finger movements. The bachelor thesis focuses on utilizing Leap Motion sensors in real-time gesture recognition using neural networks. We used two layered bidirectional LSTM architecture to train static gestures along with dynamic gestures. The neural network was benchmarked on a publicly available ASL dataset acquiring 89.07\% using 5-fold cross-validation on 200 epochs. The architecture was ultimately trained using our dataset of 3861 samples for real-time deployment. We demonstrated that the pre-trained model is sufficient to be integrated into other applications, and we also discussed the current state of the MultiLeap library, developed for hand detection using more than one Leap Motion senzor at once. We compared results of using multiple sensors with MultiLeap with results of using one sensor.
}

\abstractCS{Zkoumání způsobů pro ovládání virtuálního prostředí je populárním cílem mnoha výzkumných prací v odvětví interakce člověka s počítačem. Jeden ze způsobů je použití Leap Motion optického senzoru, vyvíjeného specificky pro rozpoznávání pohybu ruky a prstů. Tato bakalářská práce se zaměřuje na využití Leap Motion senzorů k rozpoznávání gest v reálném čase za pomocí neuronové sítě. Využili jsme architekturu dvouvrstvé obousměrné LSTM k natrénování statických i dynamických gest. Neuronová síť byla otestovaná na veřejně dostupném ASL datasetu s výsledkem 89.07\% za použití 5-fold cross validace s 200 iteracemi. Architektura byla ve finále natrénovaná využitím našeho vlastního datasetu s 3861 vzorky pro rozpoznávání v reálném čase. Demonstrovali jsme, že náš předtrénovaný model je vhodný pro použití v jiných aplikacích a také jsme diskutovali aktuální stav MultiLeap knihovny, vyvíjené pro detekci ruky pomocí více Leap Motion senzorů najednou. Porovnali jsme výsledky více senzorů použitím MultiLeap knihovny s výsledky naměřené jedním senzorem.}
\placeForDeclarationOfAuthenticity{Prague}
\keywordsCS{rozpoznávání gest, dvouvrstvé obousměrné LSTM, MultiLeap, strojové učení, rekurentní neuronová síť, rozpoznávání v reálném čase}
\keywordsEN{gesture recognition, two-layered bidirectional LSTM, MultiLeap, machine learning, recurrent neural network, real-time recognition}
\declarationOfAuthenticityOption{1} %select as appropriate, according to the desired license (integer 1-6)
% \website{http://site.example/thesis} %optional thesis URL


%========================================================================================================
\begin{document}
%========================================================================================================
	%========================================================================================================
	\setsecnumdepth{part}
	\chapter{Introduction}\label{ch:introduction}
	\input{chapters/introduction.tex}\newpage\cleardoublepage
	%========================================================================================================
	\setsecnumdepth{all}
	\chapter{Neural Networks}\label{ch:neural_network}
	\input{chapters/neural_network.tex}\newpage\cleardoublepage
	%========================================================================================================
	\setsecnumdepth{all}
	\chapter{Gesture Recognition}\label{ch:gesture_recognition}
	\input{chapters/analysis.tex}\newpage\cleardoublepage
	%========================================================================================================
	\setsecnumdepth{all}
	\chapter{MultiLeap}\label{ch:multileap}
	\input{chapters/multileap.tex}\newpage\cleardoublepage
	%========================================================================================================
	\setsecnumdepth{all}
	\chapter{Implementation}\label{ch:implementation}
	\input{chapters/implementation.tex}\newpage\cleardoublepage
	%========================================================================================================
	\setsecnumdepth{all}
	\chapter{Experiments}\label{ch:experiments}
	\input{chapters/experiments.tex}\newpage\cleardoublepage
	%========================================================================================================
	\setsecnumdepth{all}
	\chapter{Conclusion}\label{ch:conclusion}
	\input{chapters/conclusion.tex}\newpage\cleardoublepage


\bibliographystyle{iso690}
\bibliography{mybibliographyfile}

\setsecnumdepth{all}
\appendix

\chapter{Acronyms}
% \printglossaries
\begin{description}
	\item[ANN] Artificial Neural Network
	\item[RNN] Recurrent Neural Network
	\item[BRNN] Bidirectional Recurrent Neural Network
	\item[CNN] Convolutional Neural Network
	\item[LSTM] Long Short-Term Memory
	\item[BLSTM] Bidirectional Long Short-Term Memory
	\item[DLSTM] Deep Long Short-Tzerm Memory
	\item[ReLU] Rectified Linear Unit
	\item[LMC] Leap Motion Controller
	\item[LED] Light Emitting Diode 
	\item[SVM] Support Vector Machine
	\item[MLP] Multilayer Perceptron
	\item[ASL] American Sign Language
	\item[SHREC] Shape Retrieval Contest  
	\item[API] Application Programming Interface
\end{description}


\chapter{Contents of enclosed CD}

%change appropriately

\begin{figure}
	\dirtree{%
		.1 README.md\DTcomment{the Markdown file with description}.
		.1 executables\DTcomment{the directory with executables}.
		.2 Dataset\DTcomment{the directory of the original dataset}.
		.2 TrainedModel\DTcomment{the directory of trained model}.
		.2 DataSampler.exe\DTcomment{data sampling application}.
		.2 model\_trainig.py\DTcomment{model training Python script}.
		.2 GestureApp.exe\DTcomment{gesture recognition demo application}.
		.1 src\DTcomment{the directory of source codes}.
		.1 text\DTcomment{the directory of \LaTeX{} source codes of the thesis}.
		.1 environment.yml\DTcomment{configuration file for conda environment}.
		.1 BP\_Viet\_Anh\_Tran\_2021.pdf\DTcomment{the thesis text in PDF format}.
	}
\end{figure}



\end{document}
